Name: Thomas Schindler


```{r}
library(tidyverse)
```

For this assignment I will be using the Quality of Government and Polity V Data sets


```{r}
df1 <- read.csv("PolityV.csv")
df2 <- read.csv("qog_std_ts_jan22.csv")
```

```{r}
df1
```

```{r}
df2
```
Both datasets has thousands of observations so lets limit it to just 1950

```{r}
df1<-
  df1%>%
  filter(year > "1950")

df2<-
  df2%>%
  filter(year > "1950")
```

I would like to use features from QoG to predict polity scores using OLS regression.

The only variables I need from Polity V are the variables scode, country name, year, and polity

```{r}
df1<-
  df1%>%
  select(scode, year, country, polity)
```

I want to remove cases where the polity scores is not applicable indicated by the values -88, -77, and -66

```{r}
df1<-
  df1%>%
  filter(polity != "-77")%>%
  filter(polity != "-88")%>%
  filter(polity != "-66")
```


I now need to select variables of interest for our model. From looking at the QoG codebook I will use GDP per Capita, average years of education, access to media, share of women in political office, and whether or not their is an official religion.














