Name: Thomas Schindler


```{r}
rm(list=ls())
library(tidyverse)
```

For this assignment I will be using the Quality of Government and Polity V Data sets


```{r}
df1 <- read.csv("PolityV.csv")
df2 <- read.csv("qog_std_ts_jan22.csv")
```

```{r}
df1
```

```{r}
df2
```
Both datasets has thousands of observations so lets limit it to just 1950

```{r}
df1<-
  df1%>%
  filter(year > "1950")

df2<-
  df2%>%
  filter(year > "1950")
```

I would like to use features from QoG to predict polity scores using OLS regression.

The only variables I need from Polity V are the variables scode, country name, year, and polity

```{r}
df1<-
  df1%>%
  select(scode, year, country, polity)
```

I want to remove cases where the polity scores is not applicable indicated by the values -88, -77, and -66

```{r}
df1<-
  df1%>%
  filter(polity != "-77")%>%
  filter(polity != "-88")%>%
  filter(polity != "-66")
```


I now need to select variables of interest for our model. From looking at the QoG codebook I will use GDP per Capita, percent of available students in primary school, share of women in political office, and human development.


```{r}
df2<-
  df2%>%
  select(ccodealp, year, gle_cgdpc, wdi_nerp, undp_hdi, ipu_l_sw)%>%
  drop_na()
```

We can rename variables to make more logical sense and prepare for merging data

```{r}
df2<-
  df2%>%
  rename(scode = ccodealp)%>%
  rename(gdp = gle_cgdpc)%>%
  rename(education = wdi_nerp)%>%
  rename(humanDev = undp_hdi)%>%
  rename(womenParticpation = ipu_l_sw)
```


Now we can join the datasets and perform linear regression

```{r}
df <- merge(df1,df2,by=c("scode","year"))
df
```

```{r}
model <- lm(polity ~ gdp + education + humanDev + womenParticpation, data = df)
```

```{r}
summary(model)
```





